\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-12 WOOT/Files/related_work.tex
Add introduction

\subsection{USB Attack Security}
While many USB based  attacks have been developed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received. When the  protocol masquerading attack devices, e.g., Rubbery Ducky\cite{rubber}, \cite{rubberducky2020} and USBderivery\cite{usbdriver}, are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter. Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands or data will work in these scenarios.

@@

Another kind of attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} is to eavesdrop signal to recovered the sensitive data at the physical layer. Even though the data, including the video data, could be recovered in this way, the attack for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection. To our best knowledge, we are the first to combine the host interaction with attack based on USB. Based on USB Type-C, we design Armory, a multi-mode BadUSB device\chaozu{add armory description}

>>>>

\subsection{USB Attack Security}
While many USB based  attacks have been developed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received. When the  protocol masquerading attack devices, e.g., Rubbery Ducky\cite{rubber}, \cite{rubberducky2020} and USBderivery\cite{usbdriver}, are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying. Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter. Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands will work in these scenarios.

@@

Another kind of attacks for USB \cite{JFC} is to automatically record phone-screen and monitor user's input based on  the Mobile High-Definition Link(MHL) standard. With this approach, it is able to successfully exfiltrate data without the permission on user's side. Due to the limitation of MHL standard, only data exfiltrating without other attack scropt works here, and an additional conversion tool is necessary. Others attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} are to eavesdrop signal to recovered the sensitive data at the physical layer. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection. This allows attacker to control users' devices with screen monitoring, attacks for interaction work here.
